---
title: "Answer 1 for Session1: data summary"
author: "MRC Clinical Sciences Centre (http://mrccsc.github.io/)"
date: "12/July/2016"
output: html_document
---

These exercises cover the sections of Statistics in R [Session2: data summary]("Session1_describe_the_data.md").

**Exercise 1**

- Read in the file Life_expectancy_at_birth.csv.
```{r,message=T}
 Life_exp<-read.csv("../data/Life_expectancy_at_birth.csv",header=T)
```
- How many males and females in England.
```{r,message=T}
 Eng.life.exp<-Life_exp[Life_exp$area=="England",]
 summary(Eng.life.exp)
```

- What is the mean of the life.expectancy in area England? What are the mean of the life.expectancy of Males and Females, respectively, in area England?
```{r,message=T}
 mean(Eng.life.exp[,"life.expectancy"])
 mean(Eng.life.exp[Eng.life.exp$gender=="Males","life.expectancy"])
 mean(Eng.life.exp[Eng.life.exp$gender=="Females","life.expectancy"])
```

- What are quantiles of life.expectancy in area Wales, N.Ireland, and in Scotland, respectively.
```{r,message=T}
 summary(Life_exp[Life_exp$area == "Wales",])
 summary(Life_exp[Life_exp$area == "N.Ireland",])
 summary(Life_exp[Life_exp$area == "Scotland",])
```

**Exercise 2**

- What is the probablity of a value being less than or equal to 2 for a normal distribution of mean 0 and standard deviation 1
```{r,message=T}
 pnorm(2,mean=0,sd=1)
```



